### 2024-01-28 ms.qmd
Fix priobability

```{r, results}
# Rename some of the posteriors and obtain estimates for the "learning rate" for each group and treatment. This "learning rate" consists on the slope of the posterior of the Trial parameter. The slope is the rate at which the probability of choosing the correct feeder increases with each trial. The slope is obtained by adding the posterior of the Trial parameter to the posterior of the interaction between Trial and the treatment (cort and temp). 
## 1) L. delicata
### Group = red
dar_CORTCold <- deli_red$b_Trial #Slope for treatment CORT-Cold for L. delicata, red as the right choice
dar_ControlCold <- (deli_red$'b_Trial:cortControl' + deli_red$b_Trial)
dar_CORTHot <- (deli_red$'b_Trial:tempHot' + deli_red$b_Trial)
dar_ControlHot <- (deli_red$'b_Trial:cortControl:tempHot' + deli_red$b_Trial+ deli_red$'b_Trial:cortControl' + deli_red$'b_Trial:tempHot')
### Group = blue
dab_CORTCold <- deli_blue$b_Trial
dab_ControlCold <- (deli_blue$'b_Trial:cortControl' + deli_blue$b_Trial)
dab_CORTHot <- (deli_blue$'b_Trial:tempHot' + deli_blue$b_Trial)
dab_ControlHot <- (deli_blue$'b_Trial:cortControl:tempHot' + deli_blue$b_Trial + deli_blue$'b_Trial:cortControl' + deli_blue$'b_Trial:tempHot')
## 2) L. guichenoti
### Group = red
gar_CORTCold <- guich_red$b_Trial
gar_ControlCold <- (guich_red$'b_Trial:cortControl' + guich_red$b_Trial)
gar_CORTHot <- (guich_red$'b_Trial:tempHot' + guich_red$b_Trial)
gar_ControlHot <- (guich_red$'b_Trial:cortControl:tempHot' + guich_red$b_Trial + guich_red$'b_Trial:cortControl' + guich_red$'b_Trial:tempHot')
### Group = blue
gab_CORTCold <- guich_blue$b_Trial
gab_ControlCold <- (guich_blue$'b_Trial:cortControl' + guich_blue$b_Trial)
gab_CORTHot <- (guich_blue$'b_Trial:tempHot' + guich_blue$b_Trial)
gab_ControlHot <- (guich_blue$'b_Trial:cortControl:tempHot' + guich_blue$b_Trial + guich_blue$'b_Trial:cortControl' + guich_blue$'b_Trial:tempHot')
```

@@

probright_drCORTCold <- 1/(1+exp(-deli_red$b_Intercept))

>>>>

```{r, results}
#| label: results
# Rename some of the posteriors and obtain estimates for the "learning rate" for each group and treatment. This "learning rate" consists on the slope of the posterior of the Trial parameter. The slope is the rate at which the probability of choosing the correct feeder increases with each trial. The slope is obtained by adding the posterior of the Trial parameter to the posterior of the interaction between Trial and the treatment (cort and temp). 
## 1) L. delicata
### Group = red
dar_CORTCold <- deli_red$b_Trial #Slope for treatment CORT-Cold for L. delicata, red as the right choice
dar_ControlCold <- (deli_red$'b_Trial:cortControl' + deli_red$b_Trial)
dar_CORTHot <- (deli_red$'b_Trial:tempHot' + deli_red$b_Trial)
dar_ControlHot <- (deli_red$'b_Trial:cortControl:tempHot' + deli_red$b_Trial+ deli_red$'b_Trial:cortControl' + deli_red$'b_Trial:tempHot')
### Group = blue
dab_CORTCold <- deli_blue$b_Trial
dab_ControlCold <- (deli_blue$'b_Trial:cortControl' + deli_blue$b_Trial)
dab_CORTHot <- (deli_blue$'b_Trial:tempHot' + deli_blue$b_Trial)
dab_ControlHot <- (deli_blue$'b_Trial:cortControl:tempHot' + deli_blue$b_Trial + deli_blue$'b_Trial:cortControl' + deli_blue$'b_Trial:tempHot')
## 2) L. guichenoti
### Group = red
gar_CORTCold <- guich_red$b_Trial
gar_ControlCold <- (guich_red$'b_Trial:cortControl' + guich_red$b_Trial)
gar_CORTHot <- (guich_red$'b_Trial:tempHot' + guich_red$b_Trial)
gar_ControlHot <- (guich_red$'b_Trial:cortControl:tempHot' + guich_red$b_Trial + guich_red$'b_Trial:cortControl' + guich_red$'b_Trial:tempHot')
### Group = blue
gab_CORTCold <- guich_blue$b_Trial
gab_ControlCold <- (guich_blue$'b_Trial:cortControl' + guich_blue$b_Trial)
gab_CORTHot <- (guich_blue$'b_Trial:tempHot' + guich_blue$b_Trial)
gab_ControlHot <- (guich_blue$'b_Trial:cortControl:tempHot' + guich_blue$b_Trial + guich_blue$'b_Trial:cortControl' + guich_blue$'b_Trial:tempHot')
```

@@

probright_drCORTCold <- exp(deli_red$b_Intercept)/(1+exp(deli_red$b_Intercept))
